%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.0.1, 11 September 2016) written by
% LianTze Lim (liantze@gmail.com), based on the 
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

\documentclass[10pt,letterpaper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you'll need to install
%% Academicons.ttf in your operating system's font %% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Change the font if you want to.
\setmainfont{Lato}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkBlue}{HTML}{1c304b}
\definecolor{LightBlue}{HTML}{2079c7}
%\colorlet{heading}{VividPurple}
\colorlet{heading}{DarkBlue}
\colorlet{heading-line}{LightBlue}
\colorlet{accent}{DarkBlue}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{DEVIN MATTÉ}
\tagline{Full-Stack Software Engineer}
% Cropped to square from my github page
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{devin@devinmatte.com}
  \phone{(203) 470-1323}
  \homepage{\href{https://devinmatte.com}{devinmatte.com}}
  \github{\href{https://github.com/devinmatte}{devinmatte}}
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too
}

%% Make the header extend all the way to the right, if you want. Extend the right margin by 8cm (=6.8cm marginparwidth + 1.2cm marginparsep)
\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cveventnew{Zorus Inc.}{Software Engineer}{Worked in a three person team of Software Engineers building a customer portal and corresponding server from the ground up. Worked in PHP using Slim, Javascript, Python, NGINX, MySQL and AWS.}{May 2017 -- August 2017}{Newtown, CT}

\cvsection{Education}

\cvevent{Rochester Institute of Technology}{B.S. in Software Engineering}{2016 - 2021}{}

\cvsection{Projects}

\nocite{*}

\cvproject{WebDrink Server}{\href{https://github.com/ComputerScienceHouse/WebDrink-API}{github.com/ComputerScienceHouse/WebDrink-API}}{WebDrink is Computer Science Houses web interface for interacting with our web connected vending machines. I rewrote the entire communication between the Client and the Machines by creating a RESTful API using PHP, Slim, and Doctrine.}

\divider

\cvproject{AWS Wrapper}{\href{https://github.com/SquashProjectTwo/AWS-Wrapper}{github.com/SquashProjectTwo/AWS-Wrapper}}{Created at Brickhack4, a web application that created a new UI interface for AWS, specifically EC2 by using Boto3 to immitate all the functions provided by EC2 in their current web interface. Won best use of AWS at the event.}

\divider

\cvproject{wasp}{\href{https://github.com/devinmatte/wasp}{github.com/devinmatte/wasp}}{A command line utility for generating and managing web configuration files. Including the manifest.json, bower.json, package.json and composer.json. Built in Python, and packaged for Linux. Currently managing as a multiple contributor project.}

\divider

\cvproject{Calendar Maker}{\href{https://github.com/NHSTechTeam/Calendar-Maker}{github.com/NHSTechTeam/Calendar-Maker}}{A calendar generator built for the high school I attended. A PHP web app that generated a csv file for import into Google calendar by students and faculty. I still build and maintain it.}

\divider

\cvproject{Git-Challenge}{\href{https://github.com/devinmatte/Git-Challenge}{github.com/devinmatte/Git-Challenge}}{Developed an app to rank the contributions of all users in all repositories of a GitHub org. The application can be deployed, either manually or as a container with environment variables.}

\divider

\cvproject{Coralite Woodworks LLC.}{\href{https://github.com/CoraliteWoodworks/coralitewoodworks.com}{github.com/CoraliteWoodworks/coralitewoodworks.com}}{Created and designed a website for Coralite Woodworks in Python using Flask and SQLAlchemy with a focus on search engine optimization.}

\divider

For more projects, visit \href{https://devinmatte.com}{devinmatte.com}
% \cvsection{}{Volunteer}

% \cvproject{Software Engineer}{Zorus Inc.}{Worked as one of three Software Engineers building a customer portal and corresponding “node” from the ground up. Worked in PHP using Slim, Javascript, Python, NGINX, MySQL and AWS.}

\end{document}
